Applications of limited information strategies in Menger's game

### 2016-11-30 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
fix lem 5.10

\keywords{Menger property, Menger game, \(\sigma\)-compact spaces,
limited information strategies}

@@

\begin{lemma}\label{rOmegaLemma}
  For each compact subset \(K\) of \(\mathbb R\)
  and open cover \(\mc U\) of \(R_\omega\),
  there exists a countable set \(C\) such that \([a,b]\setminus C\)
  is \(\mc U\)-finite.
\end{lemma}

\begin{proof}
  Let \(\mc V\) be the corresponding open cover of \(\mathbb R\) where
  \(\mc U\) may be obtained by removing countable sets from members of
  \(\mc V\). Choose a finite subcollection \(\mc G\) of \(\mc V\) which
  covers \(K\), and then note that the corresponding finite subcollection
  \(\mc F\) of \(\mc U\) covers \([-n,n]\setminus C\) where \(C\) is the
  finite union of the countable sets removed from sets in \(\mc G\)
  to obtain the sets in \(\mc F\).
\end{proof}

>>>>

\keywords{Menger property, Menger game, , \(\sigma\)-compact spaces,
limited information strategies}

@@

\begin{lemma}\label{rOmegaLemma}
  For each compact subset \(K\) of \(\mathbb R\)
  and open cover \(\mc U\) of \(R_\omega\),
  there exists a countable set \(C\) such that \(K\setminus C\)
  is \(\mc U\)-finite.
\end{lemma}

\begin{proof}
  Let \(\mc V\) be the corresponding open cover of \(\mathbb R\) where
  \(\mc U\) may be obtained by removing countable sets from members of
  \(\mc V\). Choose a finite subcollection \(\mc G\) of \(\mc V\) which
  covers \(K\), and then note that the corresponding finite subcollection
  \(\mc F\) of \(\mc U\) covers \(K\setminus C\) where \(C\) is the
  finite union of the countable sets removed from sets in \(\mc G\)
  to obtain the sets in \(\mc F\).
\end{proof}
